Cultural Evolution of Conservation Behavior at the Intersection of Working

### 2020-12-11 DissertationProposal/DissertationProposal.Rmd
deforestation Map

Similar to community-based conservation areas, new efficient technologies have the potential to mitigate natural resource degradation while benefiting human populations, but rely greatly on community buy-in. Adoption of these technologies may diffuse and become ubiquitous within a population [@bollinger2012peer]. This is, however, not always the case. The reasons for if and when an individual adopts a new technology, especially in the contexts of conservation, are often unclear [@smith2014early]. Even in cases where a technology does spread within a population, the specific use behavior and use outcome may become so greatly modified along the transmission chain that the population level result is unrecognizable from the original intent [@lewis_transmission_2012; @mcguigan_over-imitation_2011]. Theoretical insights and controlled empirical research give suggestions for how intended technological adoption outcomes may be more likely to be retained during transmission from individual to individual or group to group. So far, these insights are yet to be validated empirically in a conservation context where technology adoption has real impacts for individuals, communities, and the environment, and those impacts may affect future adoptions [@king2007use; @muthukrishna_when_2016].

@@

* Objective 1: Create an agent based model to theoretically test whether cultural group selection via success copying or direct competition results in greater conservation adoption and better environmental outcomes, particularly in environmental contexts where solitary groups fail to cooperate.

@@

@@

```{r mapp, echo=FALSE, fig.cap="Satellite map of Pemba Island, Tanzania. Three marked locations are the wards which will be surveyed for fuel-efficient cookstove copying fidelity and outcomes.", out.width = "75%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/InsetMap.png")
```

>>>>

Similar to community-based conservation areas, new efficient technologies have the potential to mitigate natural resource degradation while benefiting human populations, but rely greatly on community buy-in. Adoption of these technologies may diffuse and become ubiquitous within a population [@bollinger2012peer]. This is, however, not always the case. The reasons for if and when an individual adopts a new technology, especially in the contexts of conservation, are often unclear [@smith2014early]. Even in cases where a technology does spread within a population, the way individuals use the technology may change dramatically from person to person so that the population level result is unrecognizable from the original intent [@lewis_transmission_2012; @mcguigan_over-imitation_2011]. Theoretical insights and controlled empirical research give suggestions for how intended technological adoption outcomes may be more likely to be retained during transmission from individual to individual or group to group [@king2007use; @muthukrishna_when_2016]. So far, these insights are yet to be validated empirically in a conservation context where technology adoption has real impacts for individuals, communities, and the environment, and those impacts may affect future adoptions.

@@

* Objective 1: Create an agent-based model to theoretically test whether cultural group selection via success copying or direct competition results in greater conservation adoption and better environmental outcomes, particularly in environmental contexts where solitary groups fail to cooperate.

@@

```{r ForestCoverMap, echo=FALSE, fig.cap="Change in annual forest cover loss in original wards with CoFMAs. Change values are the difference between average annual forest cover loss from 2001 - 2010 and the average annual forest cover loss from 2010 - 2018.", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch2/DeforestationMap.png")
```

@@

```{r mapp, echo=FALSE, fig.cap="Pemba Island, Tanzania. Three marked locations are the wards which will be surveyed for fuel-efficient cookstove copying fidelity and outcomes.", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/InsetMap.png")
```
